Topology and experimental distinguishability

### 2017-07-29 Articles/TopologyAndExperimentalDistinguishability/article.tex
Removing unused symbols and other minor edits

\documentclass[review]{elsarticle}

@@

\usepackage{amsmath, amsthm, amsfonts}
\usepackage[only,llbracket, rrbracket,llparenthesis,rrparenthesis]{stmaryrd} 
\usepackage{MnSymbol,centernot}

% Symbol for "implies" and "not implies"
\def\imp{\Rightarrow}
\def\nimp{\nRightarrow}

% Symbol for "compatibility" and "incompatibility"
\def\comp{\doublefrown}
\def\ncomp{\ndoublefrown}

@@

 \theoremstyle{definition}
 \newtheorem{defn}{Definition}[section]
\newtheorem{exmp}{Example}[section]
\theoremstyle{remark}
\newtheorem*{rem}{Remark}
\modulolinenumbers[5]

@@

The successful use of mathematical ideas in experimental sciences is long established and celebrated \cite{wigner}. Topology is perhaps the most widespread, either directly\cite{rashevsky, chichilnisky} or as a foundation to other tools\cite{nakahara}.  This leads one to ask, why is it so successful? What property is captured by topological spaces that is so fundamental for scientific investigation?

>>>>

\documentclass[preprint]{elsarticle}

@@

\usepackage{amsmath, amsthm, amsfonts}
\usepackage[only,llbracket, rrbracket,llparenthesis,rrparenthesis]{stmaryrd}

@@

\theoremstyle{definition}
\newtheorem{defn}{Definition}[section]
%\newtheorem{exmp}{Example}[section]
\theoremstyle{remark}
\newtheorem*{rem}{Remark}
\modulolinenumbers[5]

@@

The successful use of mathematical ideas in experimental sciences is long established and celebrated~\cite{wigner}. Topology is perhaps the most widespread, either directly~\cite{rashevsky, chichilnisky} or as a foundation to other tools~\cite{nakahara}.  This leads one to ask, why is it so successful? What property is captured by topological spaces that is so fundamental for scientific investigation?
